---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# geonet

<!-- badges: start -->
<!-- badges: end -->

The goal of geonet is to provide a tool for the estimation of the intensity
function of a spatial point process on a geometric network. It makes use of
generalized additive model (GAM) theory and has a similar workaround. In comparison
to other methods, it allows to include external and internal covariates in
the model, see the example below.

## Installation

You can install the released version of geonet from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("geonet")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("MarcSchneble/geonet")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(geonet)
library(spatstat.data)

X <- as_gnpp(chicago)
delta <- 10
formula <- X ~ marks + x + y

model <- intensity_pspline(X, formula = formula, delta = delta,
                           scale = list(x = 1/1000, y = 1/1000))
summary(model)
plot(model)
```
